The Three-HITs Theorem\footnote{This work was partially supported by COST Action CA15123.}

### 2017-03-22 Paper/Paper.tex
Added part on function extensionality required for lemma 13 and 14

\newcommand{\fpath}[0]{\> @ \>}
\newcommand{\conc}[0]{\bullet}
\newcommand{\comp}[0]{\circ \,}

@@

\newcommand{\coeq}[0]{\Boperator{coeq}}
\newcommand{\inC}[0]{\Boperator{inC}}
\newcommand{\glueC}[0]{\Boperator{glueC}}

@@

>>>>

\newcommand{\fpath}[0]{\> \Box \>}
\newcommand{\conc}[0]{\bullet}
\newcommand{\comp}[0]{\circ \,}

@@

\newcommand{\FE}[0]{\Boperator{FE}}
\newcommand{\funext}[0]{\Boperator{FunExt}}
\newcommand{\coeq}[0]{\Boperator{coeq}}
\newcommand{\inC}[0]{\Boperator{inC}}
\newcommand{\glueC}[0]{\Boperator{glueC}}

@@

Lastly, we need function extensionality for the proof.
Let us first introduce some notation.

\begin{definition}
Let $A, B$ be types, let $f, g : A \rightarrow B$ be maps, and let $x : A$ be a point of $A$.
Then for all $e : f = g$ we define a path $e \fpath x : f \> x = g \> x$ using path induction which sends $\refl$ to $\refl$.
\end{definition}

\begin{definition}
Given are types $A, B$ and two maps $f, g : A \rightarrow B$.
Then we define the type $\funext$, of which the inhabitants represent proofs of function extensionality, as follows
\[
\funext = (\prod (x : A), f \> x = g \> x) \rightarrow f = g.
\]
\end{definition}

We will assume that we have an inhabitant $\FE : \funext$ such that for $p : \prod (x : A), f \> x = g \> x$ and $x : A$ we have
\[
(\FE \> p) \fpath x = p \> x.
\]
In homotopy type theory function extensionality can be proved by assuming univalence \cite{UnivalenceFE} or by assuming the existence of an interval object \cite{IntervalFE}.
